---
title: "Demographics"
subtitle: "2024"
author: ""
date: ""
output: html_document
---

```{r, message = FALSE, echo = FALSE,results='hide', warning=FALSE}
library(here)
library(kableExtra)

# Inherit plots
knitr::knit_child(here("anvilPoll2024MainAnalysis.Rmd"))
# Import functions to stylize plots
source(here("resources/scripts/shared_functions.R"))
```

<br>

# Highest Degree

```{r, message=FALSE, echo=FALSE}
degreePlot
```

## Takeaway

Most of the respondents have a PhD or are currently working on a PhD, though a range of career stages are represented.

<br>

# Kind of Work

```{r, message = FALSE, echo = FALSE}
kowPlot
```

## Takeaway

Only a few responses report project management, leadership, or administration as their only kind of work. This increases our confidence that this won't confound later questions asking about usage of datasets or tools.

## Potential Follow-up

  - Use this together with other info to try to cluster respondents/users into personas.

<br>

# Institutional Affiliation

```{r, message=FALSE, echo = FALSE}
instTypePlot
```

## Takeaway

Most of the individuals using the AnVIL report being affiliated with a research intensive institution.

## Potential Follow-up

  - Does industry not being represented in this sample of returning users generalize to the larger AnVIL user base? If so, why?

<br>

# Consortia Affiliations

Of `r nrow(resultsTidy)` responses, `r sum(!is.na(resultsTidy$ConsortiaAffiliations))` provide an affiliation, with `r nrow(consortiaTable)` unique affiliations represented across those responses (respondents could select more than one consortium). The following table shows the most represented consortia.

```{r, message = FALSE, echo = FALSE}
kableExtra::kable(consortia_df, table.attr = "style='width:20%;'")
```
