---
title: "Returning Users"
subtitle: "2025"
author: ""
date: ""
output: html_document
---

```{r, message = FALSE, echo = FALSE,results='hide', warning=FALSE}
library(here)

# Inherit plots
knitr::knit_child(here("anvilPoll2025MainAnalysis.Rmd"))
# Import functions to stylize plots
source(here("resources/scripts/shared_functions.R"))
```

<br>

# Length of Use of the AnVIL

```{r, message = FALSE, echo = FALSE}
timeUsePlot
```

## Takeaway

We observe a fairly even sampling of the returning users with regards to the number of years they've been using the AnVIL

<br>

# Foreseeable Computational Needs

```{r, message=FALSE, echo=FALSE, warning=FALSE}
compNeedsPlot
```

## Takeaway

Of the `r nrow(resultsTidy %>% filter(UserType == "Returning User"))` returning users, all `r 50 - sum(is.na(resultsTidy$NeededResources))` provided an answer to this question. The most common response here is needing large amounts of storage.

## Potential Follow-up

  - What do we see in other responses from the "don't know" responses?

<br>

# Recommendation Likelihood

```{r, message = FALSE, echo = FALSE}
recLikePlot
```

## Takeaway

There's a fairly bimodal distribution here with users either extremely likely or only moderately likely to recommend the AnVIL.

## Potential Follow-up

  - What do we see in other responses from those who are extremely likely to recommend the AnVIL to a colleague? e.g., Are they part of a consortium?
  - What do we see in other responses from those who are only moderately or not at all likely to recommend the AnVIL?
